\documentclass[12pt, letterpaper, twoside]{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper]{geometry}
\usepackage{array}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{ragged2e}
\usepackage{gensymb}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{scrextend}

\newcommand{\cfootnote}[1]{\footnote{\centering #1}}
\title{Does having power make one happy?}
\author{Simon Freiermuth \\ \href{mailto:simon@freiermuth.org}{simon@freiermuth.org}}
\date{\today}

\begin{document}

%\begin{titlepage}
\maketitle
%\end{titlepage}

\begin{flushleft}

Initially one might assume that more power gives happiness and satifaction to those holding it,
because power gives the possibility to influence or shape things to one's liking.
If one can make decisions then the assumption would be that these decisions lead to greater happiness for oneself.

In \textit{Things fall apart} having power did not make Okonkwo happy, for instance in order to maintain his reputation,
he believed that he had to kill Ikemefuna, his adopted son who he liked. For Okonkwo power was the same as 'manliness' and physical power.
These were the strengths that allowed him to build his wealth and his position in the clan.\\

The missionaries came with a different form of power, the power of conviction. That power might have made some of them happier.
It won't help them when they are on their deathbed and they realise that the atheists were right.

When the missioners built their church in the evil forest and survived, the villagers were split in their opinion on how to react.
some took the missionaries survival as a proof that they are right and maybe worth following.
Okonkwo belonged to those against this new influence. The success of the missionaries threatened his position
in particular because his son Nwoye decided to convert to christianity

Having done terrible things to maintain his power first and finally losing it anyways when the english seem to take control of his clan
Okonkwo didn't see any other option than to hang himself. He had lost everything he couldn't even be buried according to his
peoples normal customs.

The higher you climb the further you fall.

\hfill

Another example of a warrior is McLendon in \textit{Dry September}.

He wasn't happy either, although he seemed to have all the power.
He seems to be frustrated, his glory days as an army officer are clearly over, he is looking for something to do.
In the barbershop he is initiating the lynch mob a bit like a bully on the schoolyard. The group of men is hunting and killing a black man
who is accused of raping a ~40 year old white woman.
When McLendon comes home after the murder he doesn't seem any happier, he is mad at his wife for not cooking food and for not expecting him.

\pagebreak

In \textit{To Kill a Mockingbird}, in a very similar setting, a lot of factual power lies in the hands of the 'Southern white godess'
when she accuses a black man of having raped her. While she receives a lot of attention it doesn't make her happier,
she remains alone and unloved.


\hfill

Conclusion: Power as such does not make you happy, if you need to defend your position with immoral means then it will burden you.
if you lose it you might be worse off than if you never had it to begin with.
Power comes with responsibility, responsibility to take decisions that could have negative consequences for other people.
That creates a lot of pressure (if you care).
Burnouts are a great example of that, higher up employees in corporations often experience this.
If your objectives or needs are ones that cannot be reached by the means of power for instance being truly loved
you will not become happier with more power. Power might make you more attractive to some, that is fun but it increases what is
at stake when such a position is lost.

\hfill

(Wordcount: 575)

\end{flushleft}

\end{document}
