\documentclass[12pt, letterpaper, twoside]{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper]{geometry}
\usepackage{array}
\usepackage{booktabs} % For prettier tables
\usepackage{ragged2e}
\usepackage{gensymb}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{scrextend}

\title{The Student's Responsibilities}
\author{Simon Freiermuth \\ \href{mailto:simon@freiermuth.org}{simon@freiermuth.org}}
\date{30 April, 2020}

\begin{document}

%\begin{titlepage}
\maketitle
%\end{titlepage}

\begin{flushleft}

\begin{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Start
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \item[HILDEGARD]	Wow, this is amazing! This is my chance to take action and make a difference!

    \item[WILHELM] 	Hi Hildegard, What are you so exited about?

    \item[HILDEGARD]	I'm going to be the class rep!

    \item[WILHELM] 	Why would you want that?

    \item[HILDEGARD]	To make a difference here at school.

    \item[WILHELM] 	Do you really think you'll actually influence the decisionmakers?

    \item[HILDEGARD]	What do you mean by "influence the decisionmakers"? It says right here that if i
			win i'll be the one making the decisions, or at least some of them.

    \item[WILHELM]	No, the only thing you'll be doing is occasionally stand in front of the class and
			try to tell the class what decision have been made by the grown-ups, while the class
			is doing anything but paying attention.

    \item[HILDEGARD]	Stop being such a negative, irritating bastard! Can't you let anyone be exited about stuff?

    \item[WILHELM]	I'm right though.

    \item[HILDEGARD]	Is that all you've got?

    \item[WILHELM]	Being right? isn't that all that matters?

    \item[HILDEGARD]	First of all you're not right, second, There's more stuff that matters.
			and do you think it's better not to do anything? Do you think we should just let
			those old meatbags decide about our future? Do you think it's better if they impose their
			traditional old values on us and our society, regulate, restrict and ruin the fun?

    \item[WILHELM]	(\textit{ironic}) Wow, what a speech, Hildi, so you actually wanna go in there and do shit.

    \item[HILDEGARD]	If you would stop being so damn negative, maybe you might achieve something too someday!

    \item[WILHELM] 	So you're asking questions, but do you have any real arguments or goals that could warrant
			such an effort? anything that could make me support you in your quest?

    \item[HILDEGARD]	I have so many ideas I'm gonna explode! I know you're vegetarian and that you always complain
			about the food in the canteen, how about we change someting there? I will fight for fresh
			vegetables and fruits for every student and teacher! As you know an apple a day keeps the
			doctor away.

    \item[WILHELM] 	Well you can talk like a politician, that's for sure, I guess I will support you then
			but I have to go to my next lesson now, bye.




\end{itemize}

\end{flushleft}
\end{document}
